---
title: "CSE 3056 J Component"
author: 
       - "Lakshmi Sairam Kakarla"
       - "K Uday"
       - "M Nivas"
output: html_notebook
---

## Loaading required packages
```{r}
rm(list=ls())
library(ggplot2)
library(dplyr)
```

# Data Preprocessing
## Loading the dataset
```{r}
online_data<-read.csv("online_shoppers_intention.csv")
head(online_data)
```

```{r}
str(online_data)
```

Checking for missing data
```{r}
sum(is.na(online_data))
```

The data set has no missing information. 
Weekend and Revenue are to be converted into factors.
Operating System, Browser,Region,Traffic Type also needs to be converted into factors
```{r}
online_data$Revenue<-as.factor(as.numeric(online_data$Revenue))
online_data$Weekend<-as.factor(as.numeric(online_data$Weekend))

online_data$OperatingSystems<-as.factor(online_data$OperatingSystems)
online_data$Browser<-as.factor(online_data$Browser)
online_data$Region<-as.factor(online_data$Region)
online_data$TrafficType<-as.factor(online_data$TrafficType)
```

```{r}
summary(online_data)
```

## Exploratory Data Analysis
```{r}
revenue_Ratio<-table(online_data$Revenue)
labels<-c(paste("No ",as.character(100*round(revenue_Ratio[1]/(revenue_Ratio[1]+revenue_Ratio[2]),2))),paste("Yes ",as.character(100*round(revenue_Ratio[2]/(revenue_Ratio[1]+revenue_Ratio[2]),2))))
pie(revenue_Ratio,labels=labels,clockwise = TRUE)
```
Around 15 of the total user activity recorded is of the revenue generating nature. This must be considered while dealing with classification algorithms, due to the existence of Majority Class. Based on the given information, using Majority class model, we would achieve an accuracy of around 85%. This would also be a base case for our classification models.
```{r}
plot(online_data$PageValues,col=online_data$Revenue)
```

